---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Overview

<!-- badges: start -->
<!-- badges: end -->

The goal of __modEval__ package is to allow users to perform statistical model evaluation and comparison. Package developed as part of the requirements of the package development course offered by [__Curso-R__](https://curso-r.com/).

## Installation

You can install the development version of modEval from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("TEDS-91/modEval")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}

library(modEval)

## Model evaluation - metrics

predicted <- data_template$`Full Model`

observed <- data_template$observed

model_eval(obs_values = observed, pred_values = predicted)

```



# The "model_eval_ui()" function

If you run __model_eval_ui()__ a graphical user interface will pop up on your screen. It is a shiny application where you are able to download a template __.xlsx__ file, fill it up with your own data and upload the __.xlsx__ to feed to the app. 
