---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# modEval

<!-- badges: start -->
<!-- badges: end -->

The goal of __modEval__ package is to allow users to perform statistical model evaluation and comparison. 

## Installation

You can install the development version of modEval from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("TEDS-91/modEval")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}

library(modEval)

## Model evaluation - metrics

predicted <- data_template$`Full Model`

observed <- data_template$observed

model_eval(obs_values = observed , pred_values = predicted)
```


```{r, warning = FALSE, message = FALSE}

## Predicted vs Observed

plot_pred_obs(data_template)

```

# The "run_modelEvalUI()" function

If you run __run_modelEvalUI()__ a graphical user interface will pop up in your screen. It is a shiny application where you are able to download a template __.csv__ file, fill it up with your own data and upload the __.csv__ to feed to app. 
